### 2018-11-26 2018_nips_vigil_poster/main.tex
new update VIGIL poster

\headerbox{MAC failures examples on CLEVR}{name=baseline, column=1, below=dataset}{
	{
	}

		{

	}
}

>>>>

\headerbox{MAC failures examples on CLEVR}{name=baseline, column=1, below=dataset}{

	\begin{figure}[H]
	\centering
	\subfloat[]{{
			\includegraphics[width=0.9\textwidth]{../img/fail_mac_cogent_b_shape.png}
			\label{subfig:pendulum_picture}
	}}

	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
	\label{fig:fail_mac_shape}
\end{figure}
	\begin{figure}[H]
	\centering
	\subfloat[]{{
			\includegraphics[width=0.9\textwidth]{../img/fail_mac_cogent_b_color.png}
			\label{subfig:pendulum_picture}
	}}

	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}
    \label{fig:fail_mac_color}
\end{figure}

}
